Geometry of Ranked Nearest Neighbour Interchange Space of Phylogenetic Trees

### 2020-01-12 rnni_convexity.tex
rewording of the convexity dfn

We use the notation $d(T, R)$ throughout the paper to denote the graph distance between trees in $\rnni$, that is, $d(T, R)$ is the length of a shortest $\rnni$ path between tree $T$ and $R$.

>>>>

We use the notation $d(T, R)$ throughout the paper to denote the graph distance between trees in $\rnni$, that is, $d(T, R)$ is the length of a shortest $\rnni$ path between tree $T$ and $R$.
An important geometric property analysed in this paper is whether trees from a certain class are connected but shortest paths that do not leave the class.
We say that a subset $S$ of trees is \emph{convex} if every pair of trees from $S$ is connected by a shortest path that completely stays within $S$.
